Making sure the variances converge with 3 circles

### 2024-07-22 Two_var3.Rmd
Two_var with 3 circles

---
title: "Making sure the variances converge"
output:
  pdf_document: default
  html_document: default
date: "2024-07-12"
---

@@

res1_nb <- MonteCarlo(n, 10000, circle_nb)
# Just one circle to begin with

@@

```{r}
cat("Monte Carlo variance:", res1_nb)
# Examples:
# Monte Carlo variance: 2789037
# Monte Carlo variance: 2827317
```

@@

res2_nb <- MC_boot(n, B1 = 1000, B2 = 400, f = circle_nb)
# Just one circle to begin with

@@

```{r}
cat("Mean of the variance of bootstrap samples:", res2_nb)
# Examples:
# Mean of the variance of bootstrap samples: 2845120
# Mean of the variance of bootstrap samples: 2851631
```

```{r}
cat("We get a difference of: ", 100*(max(res1_nb,res2_nb)-min(res1_nb,res2_nb))/min(res1_nb,res2_nb), "%", sep = "")
# Examples:
# We get a difference of: 2.01084%
# We get a difference of: 0.8599411%
```

@@

res1_vol <- MonteCarlo(n, 10000, circle_vol)
# Just one circle to begin with

@@

res2_vol <- MC_boot(n, B1 = 1000, B2 = 400, f = circle_vol)
# Just one circle to begin with

>>>>

---
title: "Making sure the variances converge with 3 circles"
output: 
  pdf_document: default
date: "2024-07-22"
---

@@

res1_nb <- MonteCarlo(n, 10000, circle3_nb)
# 3 circles

@@

```{r}
cat("Monte Carlo variance:", res1_nb)
# Examples:
# Monte Carlo variance: 
```

@@

res2_nb <- MC_boot(n, B1 = 1000, B2 = 400, f = circle3_nb)
# 3 circles

@@

```{r}
cat("Mean of the variance of bootstrap samples:", res2_nb)
# Examples:
# Mean of the variance of bootstrap samples:
```

```{r}
cat("We get a difference of: ", 100*(max(res1_nb,res2_nb)-min(res1_nb,res2_nb))/min(res1_nb,res2_nb), "%", sep = "")
# Examples:
# We get a difference of: 
```

@@

res1_vol <- MonteCarlo(n, 10000, circle3_vol)
# 3 circles

@@

res2_vol <- MC_boot(n, B1 = 1000, B2 = 400, f = circle3_vol)
# 3 circles
